\renewcommand{\thesection}{\Alph{section}}
\section{Product perspective}\label{sec:product_perspective}
\subsection{Scenarios}\label{subsec:scenarios}
\subsubsection{Scenario 1: Mr.Spongebob registers on the platform}\label{subsubsec:scenario_1}
Mr.Spongebob, a final-year student at the University of Bikini Bottom, is looking for an internship to practice the knowledge he's gained. 
To do so, he asks advice from Professor Puff, who suggests using the Students\&Companies platform to search for internship opportunities.
Following her advice, Mr.Spongebob registers as a student on the platform, selecting the University of Bikini Bottom from the list of 
universities and verifying his student status with his educational email and password. Then, he fills in all the required personal information,
including his name, date of birth, and other details. He also inserts keywords to describe his skills and the fields of jobs he might interested 
in. Finally, after uploading his CV, which contains all the necessary information and details, Mr.Spongebob completes his registration and 
can begin searching for internships. Meanwhile, Professor Puff, who oversees internship activities using the official account of the University of 
Bikini Bottom, is notified of Mr.Spongebob's registration.

\subsubsection{Scenario 2: Mr.Krabs publish an internship offer}\label{subsubsec:scenario_2}
Due to the rapid evolution of Technology, Mr.Krabs decides to collaborate with his competitor Mr.Plankton, on a new project. They 
plan to develop a ``Hamburger super secret formula detector'' that can detect each customer's thoughts just by looking at them, in 
this way to create the perfect personalized hamburger! To achieve this, they need to hire a student specializing in Computer Vision and
AI to study the visual data. So Mr.Krabs logs into the Students\&Companies platform using the official company account
and navigates to the ``Publish Internship'' section to create a new announcement. He fills in all the required information: the title of the 
internship as ``Computer Vision and AI Intern'', location as ``Krusty Krab Technology Lab'' at Bikini Bottom, role as ``Intern'', application deadline 
as ``25th December 2024'', number of positions as ``2'', duration as ``6 months'', employment type as ``full-time'', description as ``We are looking for a 
student who can contribute to the development of the Hamburger super secret formula detector by Developing algorithms that collect and analyze 
visual data. The candidate should also love hamburgers'' and required skills such as ``Computer Vision, AI, Python, and Deep Learning''. 
After that, Mr.Krabs published the internship offer, which can be seen in the ``Internship Offers Published'' section. Immediately after 
the publication, he receives a notification of recommended student profiles that may match the offer requirements.

\subsubsection{Scenario 3: Mr.Patrick searches internship}\label{subsubsec:scenario_3}
In the last semester of his studies, Mr.Patrick is very worried about finding an internship before completing his degree in Food Engineering. 
At this point, he remembers the Students\&Companies platform, which he used to find an internship at the beginning of his studies, so he decides 
to take another look at the platform. He logs in and updates his profile and CV, adding the new skills he has acquired during his master’s degree.
He navigates to the search bar and types ``Hamburger'' to look for internships related to hamburger studies. When he doesn’t find anything that 
interests him, he scrolls through the recommended internships list. Finally, he finds Mr.Krabs' posting and becomes very interested in the 
project, so he applies for the internship and waits for the company's response. After applying, he can check the status of his application in 
the ``Internship'' section.

\subsection{Scenario 4: Krusty Krab Technology Lab Interview}\label{subsubsec:scenario_4}
After the application deadline, Mr.Krabs and Mr.Plankton review all the applications received for the intern position. They select the
candidates by reviewing their profiles and CVs, and then send them an invitation for an interview. For the first round of interviews, Mr.Plankton
decides to formulate a set of short questions to know more about the candidates' skills and experiences. In the form he also includes the date,
time and location of the interview and the necessary information to better prepare the candidates. After sending the invitations, the candidates
selected for the interview receive a notification from the platform, who is not selected will receive a notification of rejection. At the end of 
the interview, Mr.Plankton evaluates the candidates and discusses with Mr.Krabs to decide who to hire. Finally, they send an offer to the
best candidates and wait for their acceptance to start the internship.

\subsection{Scenario 5: Ms.Sandy start her internship}\label{subsubsec:scenario_5}
Ms.Sandy is very passionate about space and is thrilled to have been selected for an internship at the Underwater Space Agency. She receives 
and accepts an offer from the company. At the same time, the Bikini Bottom University of Aerospace's professor Manta received the notification
about the new activity started by Sandy. However, she is a bit anxious, so she logs into the platform and navigates to the ``Internship'' 
section to find her assigned mentor's profile. She starts a chat with him to ask some questions about how she should prepare in the coming days
and for any advice he can give her to have a good start in the internship.

\subsection{Scenario 6: Mr.Squidward finished his internship}\label{subsubsec:scenario_6}
At the end of his internship at the ``Krusty Krab Technology Lab'' as a data science intern, Mr.Squidward is surprised by the experience 
he has gained, even though he has several complaints about the heavy workload. He decides to leave a warm message for Mr.Krabs and Mr.Plankton 
to thank them for the opportunity. After that, he navigates to the ``Internship'' section to add a review of his internship experience and rate 
the company. It is also the section where he can check the feedback left by his mentors regarding his internship, which is only visible to the 
company and the university.

\subsection{Scenario 7: Track the internship activities}\label{subsubsec:scenario_7}
As the internship period progresses, Professor Puff is responsible for overseeing the students' activities at the University of Bikini Bottom. 
She is curious to know how the students are doing in their internships, particularly Mr.SpongeBob, who is using the platform for the first time. 
She logs into the platform with the university credentials and looks at the list of students, searching for SpongeBob's name. She finds, 
in his active internship section, that he has been selected for an internship at the ``Krusty Krab Technology Lab''. By reading the feedback 
left by the company throughout the different stages of the internship, she is very glad to see that SpongeBob is doing well in the field he is 
passionate about!